---
title: Task 3(2) - Statistical Methods Project - Vo Van Viet, Khong Minh Duc, Cao
  Ngoc Bao Long
output:
  html_document:
    df_print: paged
---
First, we need to import the library "mosaic"

```{r}
library(mosaic)
```
Then, we assign the data from exersice 5.36
```{r}
compre <- c(60,76,76,90,81,75,95,98,88,73,90,66,91,83,100,85,76,69,91,78)
compre
```
Computing the mean of 10000 bootstrap samples by resampling the dataset 
```{r}
mean_each <- do(10000) * mean(resample(compre,replace=TRUE))
head(mean_each)
```
Sketching the histogram of mean of each bootstrap sample
```{r}
histogram(mean_each[["mean"]])
```
Computing the mean and the standard deviation of all bootstrap samples
```{r}
ybar<-mean(mean_each[["mean"]])
ybar
s <- sd(mean_each[["mean"]])
s
```
Assigning the sample size, significane level
```{r}
n <- length(compre)
alpha <- 0.05  
```
The hypothesis test: H0 <= 80 vs. Ha > 80 
```{r}
mu0=80
```
Computing the Test Statistic and Critical Value
```{r}
ts = (ybar-mu0)/(s/sqrt(n))#test statistic
ts
t.alpha = qt(1-alpha,df=n-1)  #critical value
t.alpha
```
Testing:
```{r}
if (ts > t.alpha) print("reject H0") else print("fail to reject H0")
```
P_value
```{r}
pval = pt(ts, df=n-1, lower.tail = FALSE)
pval #upper tail p-value
```

From Exersice 5.37
Calculating the p-value of that case
```{r}
ybar37 <- mean (compre)
s37 <- sd(compre)
ts37 = (ybar-mu0)/(s/sqrt(n))
pval37 = pt(ts37, df=n-1, lower.tail = FALSE)
pval37
```
As we can see the p-value from 5.37 and the p-value are approximately similar

