---
title: "Task 1 - Statistical Methods Project - Vo Van Viet, Khong Minh Duc, Cao Ngoc Bao Long"
output:
  html_document:
    df_print: paged
---
Exercise 5.8

Firstly, we assign the sample size, sample standard deviation, sample mean and the confidence level

```{r}
n=15            #sample size
s=12.5          #sample standard deviation
ybar=7.2        #sample mean
alpha <- 0.01   #assign the confidence level
```

Next, we compute the lower and the upper of the interval
```{r}
t.halfalpha= qt(p=1-(alpha/2),df=n-1) #compute t of half alpha and df
E=t.halfalpha*s/sqrt(n)               #compute margin of error
lower= ybar-E                         #calculate the lower of the interval
upper= ybar+E                         #calculate the upper of the interval
```

```{r}
cat("confidence interval: between",lower ,"and", upper )
```


Exercise 5.9:

Firstly, we assign the sample size, sample standard deviation, sample mean and the confidence level
```{r}
n=200           #sample size
s=1.3           #sample standard deviation
ybar=2.8        #sample mean
alpha <- 0.05   #assign the confidence level
```

Next, we compute the lower and the upper of the interval
```{r}
z.halfalpha= qnorm(1-alpha/2) #compute t of half alpha and df
E=z.halfalpha*s/sqrt(n)       #compute margin of error
lower= ybar-E                 #calculate the lower of the interval
upper= ybar+E                 #calculate the upper of the interval
```
```{r}
cat("confidence interval: between",lower ,"and", upper )
```


Exercise 5.39:
a/ Firstly, we assign the data, the confidence level and compute the sample size, sample standard deviation, sample mean
```{r}
tire <- c(25,27,35,42,28,37,40,31,29,33,30,26,31,28,30) #assign the data
n=length(tire)      #sample size
n
s=sd(tire)          #sample standard deviation
s
ybar=mean (tire)    #sample mean
ybar
alpha <- 0.01       #assign the confidence level
```

Next, we compute the lower and the upper of the interval
```{r}
t.halfalpha= qt(p=1-(alpha/2),df=n-1) #compute t of half alpha and df
E=t.halfalpha*s/sqrt(n)               #compute margin of error
lower= ybar-E                         #calculate the lower of the interval
upper= ybar+E                         #calculate the upper of the interval
```

```{r}
cat("confidence interval: between",lower ,"and", upper )
```

b/ We state the null hypothesis and the alternative hypothesis are:
H0: mu >= 35 vs. Ha: mu < 35

Then, we compute the test statistic and the critical value 
```{r}
mu0=35
ts = (ybar-mu0)/(s/sqrt(n))  #test statistic
ts
t.alpha = qt(1-alpha,df=n-1)  
-t.alpha                     #critical value
```
Next, we compare the test statistic and the critical value and conclude.
```{r}
if (ts < -t.alpha) print("reject H0") else print("fail to reject H0")
```

The result showed that the claim of that company is rejected.

Compute the lower tail p-value
```{r}
pval = pt(ts, df=n-1)
pval        #lower tail p-value
```


Exercise 5.40:

Case 1:

We state the null hypothesis and the alternative hypothesis are:
H0: mu = 35 vs. Ha: mu not equals 35

we compute the lower and upper of the interval
```{r}
alpha <- 0.05                         #assign the confidence level
t.halfalpha= qt(p=1-(alpha/2),df=n-1) #compute t of half alpha and df
E=t.halfalpha*s/sqrt(n)               #compute margin of error
lower= ybar-E                         #calculate the lower of the interval
upper= ybar+E                         #calculate the upper of the interval
```

```{r}
cat("confidence interval: between",lower ,"and", upper )
```

Next, we check whether mu0 is lie between the lower and upper tails or not and conclude
```{r}
if(mu0>lower && mu0<upper) print("fail to reject H0") else print ("reject H0")
```

case 2:
In another hand, we do the hypothesis testing:

We compared the computed test statistic from previous exercise and the new critical value and conclude 
```{r}
if (ts > t.halfalpha) print("reject H0") else print("fail to reject H0")
```

We can see that the results from 2 cases are different, so we claim that there is a contradiction 


Exercise 5.41: 
a/ Firstly, we assign the data, the confidence level and compute the sample size, sample standard deviation, sample mean
```{r}
oxygen <- c(5.1, 4.9,5.6,4.2,4.8,4.5,5.3,5.2)  #assign the data
n=length(oxygen)                               #sample size
n
s=sd(oxygen)                                   #sample standard deviation
s
ybar=mean (oxygen)                             #sample mean
ybar
```

Next, we compute the lower and the upper of the interval
```{r}                         
alpha <- 0.05                         #assign the confidence level
t.halfalpha= qt(p=1-(alpha/2),df=n-1) #compute t of half alpha and df
E=t.halfalpha*s/sqrt(n)               #compute margin of error
lower= ybar-E                         #calculate the lower of the interval
upper= ybar+E                         #calculate the upper of the interval
```
```{r}
cat("confidence interval: between",lower ,"and", upper )
```
b/ We can see 5 is included in the 95% confidence interval, but not sure that the mean is always less than 5 

c/We state the null hypothesis and the alternative hypothesis are:
H0: mu >= 5 vs. Ha: mu < 5
Then, we compute the test statistic and the critical value 
```{r}
ts = (ybar-mu0)/(s/sqrt(n))  #test statistic
t.alpha = qt(1-alpha,df=n-1)  
-t.alpha                     #critical value
```

We compare the test statistic and the critical value
```{r}
if (ts < -t.alpha) print("reject H0") else print("fail to reject H0")
```

The result showed that there is in sufficient evidence to support that the mean oxgen level is less than 5 ppm

Compute lower tail p-value
```{r}
pval = pt(ts, df=n-1)
pval #lower tail p-value
```

Exercise 5.42:

Firstly, we assign the data, the confidence level and compute the sample size, sample standard deviation, sample mean
```{r}
volumes <- c(1660,1820,1590,1440,1730,1680,1750,1720,1900,1570,1700,1900,1800,1770,2010,1580,1620,1690)
n=length(volumes)     #sample size
n
s=sd(volumes)         #sample standard deviation
s
ybar=mean (volumes)   #sample mean
ybar

```
a/
We state the null hypothesis and the alternative hypothesis are:
H0: mu <= 1600 vs. Ha: mu > 1600
Then, we compute the test statistic and the critical value 
```{r}
alpha <- 0.05                 #assign the confidence level
mu0=1600
ts = (ybar-mu0)/(s/sqrt(n))   #test statistic
ts
t.alpha = qt(1-alpha,df=n-1)  #critical value
t.alpha
```

We compare the test statistic and the critical value
```{r}
if (ts > t.alpha) print("reject H0") else print("fail to reject H0")
```
The result showed that there is in sufficient evidence to support that the average volume is greater than 1600 cubic feet

b/We compute the lower and the upper of the interval
```{r}
t.halfalpha= qt(p=1-(alpha/2),df=n-1) #compute t of half alpha and df
E=t.halfalpha*s/sqrt(n)               #compute margin of error
lower= ybar-E                         #calculate the lower of the interval
upper= ybar+E                         #calculate the upper of the interval
```
```{r}
cat("confidence interval: between",lower ,"and", upper )
```
c/ Compute the upper tail p-value
```{r}
pval = pt(ts, df=n-1, lower.tail = FALSE)
pval #upper tail p-value
```

Exercise 11.4:
First, we assign the data
```{r}
x <- c(7,12,14,22,27,33,37,39,42,49,53,61)
y <- c(10.6,16.8,23.3,12.5,91.7,67.7,130.7,110.3,147.3,138.3,142.6,151.4)
```
Then, we used the function lm() to compute the intercept and slope of the linear regression model
```{r}
RA <- lm(y~x)
RA
```
Here, we have gotten the function y= -16.505 + 3.135x.
We Sketch the scatter plot and the regression line
```{r}
plot(x, y, pch = 16, cex = 1.3, col = "blue", main = "x and y", xlab = "x", ylab = "y")
abline(lm(y~x))
```
Then, we used the least-squares prediction equation to predict y when x=40 
```{r}
xi <- 40
yi <- -16.505 + 3.135*xi
cat("The predicted y is",yi)
```

